The hidden manifold distance for functional data

### 2020-04-29 index.Rmd
starting conclusion section

The work of \cite{ChenMuller2012} was among the first in functional data analysis to consider the manifold hypothesis for functional data. A notion of the mean and variation of functional manifold data was introduced there. Of particular relevance to this work is their proposed P-ISOMAP procedure which allows for noisy functional observations. This is in contrast to the classic ISOMAP algorithm \cite{Tenenbaum2000} which assumes observations lie exactly on the manifold. This drawback to ISOMAP was also realised in \cite{Dimeglio2014} who proposed a procedure we will call robust-ISOMAP for functional data that is less sensitive to outliers. We will discuss P-ISOMAP and robust-ISOMAP in more details below.

@@

# RELATED WORK

@@

>>>>

@@

# RELATED WORK
The work of \cite{ChenMuller2012} was among the first in functional data analysis to consider the manifold hypothesis for functional data. A notion of the mean and variation of functional manifold data was introduced there. Of particular relevance to this work is their proposed P-ISOMAP procedure which allows for noisy functional observations. This is in contrast to the classic ISOMAP algorithm \cite{Tenenbaum2000} which assumes observations lie exactly on the manifold. This drawback to ISOMAP was also realised in \cite{Dimeglio2014} who proposed a procedure we will call robust-ISOMAP for functional data that is less sensitive to outliers. We will discuss P-ISOMAP and robust-ISOMAP in more details below.

@@

# CONCLUSION

In this work, we firstly challenge the existing paradigm of measuring distance for functional data. We advocated for the manifold perspective. We develop a method for estimating geodesic distances between functional manifold data. The approach relies on integrating ideas across several disciplines including manifold learning, functional data analysis, and signal processing.
